\pkg{RProtoBuf}: Efficient Cross-Language Data Serialization in \proglang{R}

### 2014-01-27 papers/jss/article.Rnw
another hyphen between nouns
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@857 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

In order to accomplish this, \CRANpkg{RProtoBuf} uses the same catch-all \texttt{proto}
schema used by \pkg{RHIPE} for exchanging \proglang{R} data with Hadoop \citep{rhipe}. This 
schema, which we will refer to as \texttt{rexp.proto}, is printed in
%appendix \ref{rexp.proto}.
the appendix.
The Protocol Buffer messages generated by \CRANpkg{RProtoBuf} and
\pkg{RHIPE} are naturally compatible between the two systems because they use the 
same schema. This shows the power of using a schema based cross-platform format such
as Protocol Buffers: interoperability is achieved without effort or close coordination.

>>>>

In order to accomplish this, \CRANpkg{RProtoBuf} uses the same catch-all \texttt{proto}
schema used by \pkg{RHIPE} for exchanging \proglang{R} data with Hadoop \citep{rhipe}. This 
schema, which we will refer to as \texttt{rexp.proto}, is printed in
%appendix \ref{rexp.proto}.
the appendix.
The Protocol Buffer messages generated by \CRANpkg{RProtoBuf} and
\pkg{RHIPE} are naturally compatible between the two systems because they use the 
same schema. This shows the power of using a schema-based cross-platform format such
as Protocol Buffers: interoperability is achieved without effort or close coordination.
